Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2023-12-01 manuscript/manuscript.Rmd
Adding putative author list

---
title: "Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre"
author: "William Kumler"
date: "`r Sys.Date()`"
output: 
  word_document:
    reference_docx: template.docx
bibliography:
- Exported Items.bib
- r-packages.bib
---

>>>>

---
title: "Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre"
author: "William Kumler, Laura T. Carlson, Wei Qin, Rachel A. Lundeen, Benedetto Barone, and Anitra E. Ingalls"
date: "`r Sys.Date()`"
output: 
  word_document:
    reference_docx: template.docx
bibliography:
- Exported Items.bib
- r-packages.bib
---
